---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# AlphaVantageQuery

The goal of AlphaVantageQuery is to query the API from Alpha Vantage (which you can find at: https://www.alphavantage.co/) for easy access to data. All you would need is a ticker symbol and an API key for more granular level data.



## Installation

You can install the released version of AlphaVantageQuery from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("AlphaVantageQuery")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r alpha_vant}
library(AlphaVantageQuery)


alpha_vant("GOOGL", frequency = "daily")      # this only returns a data frame

matrix1 = matrix(
    c(
      rep(1,3),
      rep(1,3),
      rep(1,3),
      rep(2,3),
      rep(2,3)
    ), 
    nrow = 5, ncol = 3, byrow = TRUE
  )
  with(subset(GOOGL_DAILY, GOOGL_DAILY$date > as.Date("2010-01-01")),
       {
         layout(matrix1)
         plot(date, open, type = "l", main = "GOOGL")
         lines(date, high, col = "blue", lwd = 0.3)
         lines(date, low, col = "blue", lwd = 0.3)
         
         plot(date, volume, type = "l", main = "GOOGL", col = "#108a4c")
       }
  )
```


Note that the function only returned the data frame. 
